Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-09-06 manuscript/manuscript.tex
cw edits

Once validated, the transition matrix can be decomposed into left-eigenvectors and eigenvalues,

@@

The subsequent eigenvalues $\lambda_{i>1}(\tau)$ are real with absolute values less than~$1$ and are related to the \emph{characteristic} or \emph{implied} time-scales of dynamical processes within the system~\ref{eq:its}.

>>>>

Once validated, the transition matrix can be decomposed into left eigenvectors and eigenvalues,

@@

The subsequent eigenvalues $\lambda_{i>1}(\tau)$ are real with absolute values less than~$1$ and are related to the \emph{characteristic} or \emph{implied} time-scales of dynamical processes within the system (eq.~\ref{eq:its}).
